Parsing Postfix log files

### 2008-03-08 doc/logparser.tex
Small changes

Section~\ref{parsing-algorithm} contains the core of the paper, describing
a naive parsing algorithm and the complications initially encountered which
shaped the full algorithm.  A flow chart and a discussion of the emergent
behaviour exhibited by the algorithm accompanies a comprehensive
explanation of the different stages of the algorithm.  The actions taken
during execution of the algorithm are described, followed by the process of
adding a new action.  The section concludes with an in-depth description of
the further complications discovered and their solutions which complete the
algorithm.

@@

\newpage
\section{Conclusion}

@@

A parser's ability to correctly parse it's input is extremely important;
the parser's coverage of its test log files is discussed in
\sectionref{parsing coverage}.  Both its success at parsing individual log
lines (\sectionref{log-lines-covered}) and its correctness in
reconstructing each mail's journey through Postfix
(\sectionref{mails-covered}) are described in detail, including the results
of manually verifying the correct parsing of a subset of the test log
files.

>>>>

Section~\ref{parsing-algorithm} contains the core of the paper, describing
a naive parsing algorithm and the complications initially encountered which
shaped the full algorithm.  A flow chart and a discussion of the emergent
behaviour exhibited by the algorithm accompanies a comprehensive
explanation of the different stages of the initial algorithm.  The
framework which actions and rules fit into is documented, then the actions
taken during execution of the algorithm are described, followed by the
process of adding a new action.  The section concludes with an in-depth
description of the further complications discovered and their solutions
which complete the parser.

@@

% XXX SHOULD I HAVE THIS \newpage?
\newpage
\section{Conclusion}

@@

A parser's ability to correctly parse its input is extremely important; the
parser's coverage of its test log files is discussed in \sectionref{parsing
coverage}.  Both its success at parsing individual log lines
(\sectionref{log-lines-covered}) and its correctness in reconstructing each
mail's journey through Postfix (\sectionref{mails-covered}) are described
in detail, including the results of manually verifying the correct parsing
of a subset of the test log files.
